---
title: "p8105_hw6_jf3355"
author: "Jiahao Fan"
date: "12/2/2021"
output: github_document
---

```{r}
library(tidyverse)
library(broom)
library(knitr)
library(modelr)
```

##Problem1
#Load and clean the data for regression analysis
```{r}
birthweight =
  read.csv("birthweight.csv") %>% 
  skimr::skim() %>% 
  select(skim_variable, n_missing) %>%
  knitr::kable()
birthweight  
```
There is no missing value.
```{r}
birthweight_df = 
  read.csv("birthweight.csv") %>% 
  mutate(
    babysex = recode_factor(babysex, "1" = "male", "2" = "female"),
    frace = recode_factor(frace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other", "9" = "Unkown"),
    mrace = recode_factor(mrace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other"),
    malform = recode_factor(malform, "0" = "absent", "1" = "present" )
  )
```

#Propose a regression model for birthweight
We need first find proper variable. after I run the linear regression with all variable, I choose the variables' p-value less than 0.05, which are `babysex`, `bhead`, `blength`, `delwt`, `fincome`, `gaweeks`, `mheight`, `ppwt`, `smoken` .
```{r}
fit1 = lm(bwt~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + ppwt + smoken, data =birthweight_df)
fit1 %>% 
  broom::tidy() %>% 
  select(term,estimate,p.value) %>% 
  knitr::kable()
plot1 = 
  birthweight_df %>% 
  modelr::add_residuals(fit1) %>% 
  modelr::add_predictions(fit1) %>% 
  ggplot(aes(x = pred, y = resid))+ geom_point()+labs(title = "Plot of Model Residuals against Fitted Values", x = "Fitted Values",y = "Residuals")
plot1
```
#Compare the model to two others.
fit2: One using length at birth and gestational age as predictors (main effects only)
fit3: One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
```{r}
fit2 <- lm(bwt ~ blength + gaweeks, data = birthweight_df)
fit3 <- lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = birthweight_df)
plot2 = 
  birthweight_df %>% 
  modelr::add_residuals(fit2) %>% 
  modelr::add_predictions(fit2) %>% 
  ggplot(aes(x = pred, y = resid))+ geom_point()+labs(title = "Plot2 of Model Residuals against Fitted Values", x = "Fitted Values",y = "Residuals")

plot3 = 
  birthweight_df %>% 
  modelr::add_residuals(fit3) %>% 
  modelr::add_predictions(fit3) %>% 
  ggplot(aes(x = pred, y = resid))+ geom_point()+labs(title = "Plot3 of Model Residuals against Fitted Values", x = "Fitted Values",y = "Residuals")

plot2
plot3
```

#Make this comparison in terms of the cross-validated prediction error
```{r}
cv_df = 
  crossv_mc(birthweight_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) %>% 
  mutate(
    fit1 = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + ppwt + smoken, data = .x)),
    fit2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    fit3 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = .x))
  ) %>% 
  mutate(
    rmse_fit1 = map2_dbl(fit1, test, ~rmse(model = .x, data = .y)),
    rmse_fit2 = map2_dbl(fit2, test, ~rmse(model = .x, data = .y)),
    rmse_fit3 = map2_dbl(fit3, test, ~rmse(model = .x, data = .y))
    )
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin() + labs( title = "Distribution of RMSE Values")
```
From three plot, we can see fit1 has smallest rmse compare to others.
Thus, fit1 is the best model to fit.

##Problem2
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```
#Boostraping
```{r}
set.seed(1)
bootstrap_df = 
  weather_df %>% 
  bootstrap(n = 5000, id = "strap_number") %>% 
  mutate(
    linear_models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)),
    result_log = map(linear_models,broom::tidy),
    result_r2 = map(linear_models,broom::glance)
  ) %>% 
  select(strap_number, result_log, result_r2) %>% 
  unnest(result_log, result_r2)
```
#Plot
```{r}
bootstrap_df %>% 
  filter(term == "tmin") %>% 
  ggplot(aes(x = r.squared))+geom_density()+labs(title = "Distribution of R Squared")
```
From the plot, we can see R squared is nearly normal distributed.The mean and median is `r mean(bootstrap_df$r.squared)` and `r median(bootstrap_df$r.squared)`, the standard error is `r sd(bootstrap_df$r.squared)`.

#95% CI
```{r}
ci_r2 = 
  bootstrap_df %>% 
  summarise(
  ci_lower = quantile(r.squared, 0.025),
  ci_upper = quantile(r.squared, 0.975)
  )
ci_r2
```
The lower bond is 0.8936684, and the upper bond is 0.927106.

#Plot and 95% CI of log(beta0*beta1)
```{r}
log_df = 
  bootstrap_df %>% 
  select(term, estimate) %>% 
  mutate(
    term = recode(term,`(Intercept)` = "beta0", "tmin" ="beta1")
  ) %>% 
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
  ) %>% 
  unnest(beta0,beta1) %>%
  mutate(log = log(beta0 * beta1))

log_df %>% 
  ggplot(aes(x = log))+geom_density()+labs(title = "Distribution of Log(beta0*beta1)")
ci_log = 
  log_df %>% 
  summarise(
    ci_lower = quantile(log, 0.025),
    ci_upper = quantile(log, 0.975)
  )
ci_log
```
From the plot, we can see this is nearly normal distributed. The mean and median is `r mean(log_df$log)` and `r median(log_df$log)`, the standard error is `r sd(log_df$log)`. The 95% CI is (1.964949,2.058887		).


